### 2016-11-01 paper/evaluation.tex
Updated eval text

We used the Github's Search API to fetch the top 1,000 Java projects
with at least 100 stars. The number of stars indicates the interest
and appreciation from the community to a given project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation to find relevant
projects to conduct our study.\Jbc{Subject selection is currently OK
    but I will use another way (eg Google BigQuery) to have access to
more subjects.} For each project, we detected the build manager system
based on the files located in the root directory from the project in
the following precedence: Maven (\emph{pom.xml)}, Gradle
(\emph{gradlew}), and Ant (\emph{build.xml}). From the 1,000
downloaded projects (composed by \Fix{X} Maven, \Fix{Y} Gradle,
\Fix{W} Ant, and \Fix{W} unknown projects), we selected the 154 Maven
projects that we were able to compile\Jbc{Remember to update those
numbers (download + projects) after updating the subject selection
approach.}. We noticed that we are unable to compile other subjects
because other build systems are commonly related to a particular
platform (\eg, Gradle implied Android), the build process is based on
user-defined tasks (\eg, Ant), or the project has unsolved
dependencies.

>>>>

\Jbc{Subject selection is currently OK but I will use another way (eg
Google BigQuery) to have access to more subjects.}We used the Github's
Search API~\cite{githubsearch} to fetch the top 1,000\footnote{The
    Search API imposes the limit of 1,000 results regardless of the
total number of matches from a search criteria.} Java projects with at
least 100 stars. The number of stars indicates the interest and
appreciation from the community to a given project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation to find relevant
projects to conduct our study. We detected the build manager system
based on the files located in the root directory from the project in
the following precedence: Maven (\emph{pom.xml)}, Gradle
(\emph{gradlew}), and Ant (\emph{build.xml}).\Jbc{Remember to update
the following values after updating the subject selection approach.}
From the 1,000 downloaded projects, we detected the build system of
801 subjects (composed by 216 Maven, 564 Gradle, and 21 Ant projects)
and considered \Fix{154} projects that we were able to compile.
\Fix{We noticed that we are unable to compile other subjects because of
unsolved dependencies, other build systems are commonly related to a
particular platform (\eg, Gradle implied Android), or the build
process is based on user-defined tasks (\eg, Ant).}
